---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wowr

The goal of wowr is to provide functions to interact with the [World of Warcraft API](https://develop.battle.net/documentation/api-reference/world-of-warcraft-community-api).

## Installation

You can install wowr from [Github](https://www.github.com/tutuchan/wowr) with:

```{r eval = FALSE}
remotes::install_github("tutuchan/wowr")
```

In order to use the functions in `wowr`, you need to:

+ own a Blizzard account (or create a new one), 
+ add a Blizzard authenticator (if you don't have one already), 
+ create a client on the developer portal and retrieve your client id and secret. These steps are explained in the [Blizzard documentation](https://develop.battle.net/documentation/guides/getting-started).

These values can be passed to the `wow_auth()` function or, for convenience, stored in your .Rprofile as the `BLIZZARD_CLIENT_ID` and `BLIZZARD_CLIENT_SECRET` environment variables.

## Usage

### Authentication

The `wow_auth()` function returns an authentication token that can be passed to subsequent functions.

```{r}
library(wowr)
token <- wow_auth(region = "EU")

wow_realms(token = token)
```

The token is also cached using `httr` in a `.httr-oauth` file. If you don't provide a token, `wowr` will check if there is a cached token and if there is, if it's still valid. It is recommended to provide the token as checking the validity requires a call to the Blizzard API every time.

```{r}
wow_realms()
```

### Dot parameters

Many functions take `...` parameters. They can be one of the following:

+ *token*: the token returned from `wow_auth()`,
+ *region*: a character, one of the available [regions](https://develop.battle.net/documentation/guides/regionality-partitions-and-localization),
+ *locale*: a character, one of the available [locales](https://develop.battle.net/documentation/guides/regionality-partitions-and-localization)
